---
title: "Example Dissertation"
author: 
  first: First
  last: Last
  middle: M.
  committee:
    advisora: Dr. Friendly Advisor
    advisorb: Dr. Awesome Advisor
    membera: Dr. Who
    memberb: Major Major Major Major
    memberc: Dr. Strangelove
    memberd: Dr. Doolittle
date: "June 22, 2017"
fontsize: 12pt
documentclass: report
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: UNC_thesis_template.tex
    includes: 
      in_header: example_header_include.tex
bibliography: example.bib
bibliography-style: asa
toc: true
lot: true
abstract: I have an abstract!
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction 

## Getting started

This is an example thesis .Rmd template, which, when compiled, uses the `UNC_thesis_template.tex` file to create both a `.tex` file and a `.pdf` file.

NOTE: `UNC_thesis_template.tex` is under development and does NOT (yet) meet the UNC graduate school guidelines.

You can put custom definitions in a file to be included in the .tex header. For example, putting 
```
\def\cA{{\mathcal{A}}} 
```
in `example_header_include.tex`  allow you to type `\cA` in the text which, when compiled, yields: $\cA$. Change the filename as necessary but be sure to update the filename in the YAML header.

## Another thing

I have more to say such as, "I can put a table here"

\begin{table}[ht]
\caption{This is my first table.}
\label{tab:1}
\begin{tabular}{c|c}
$\sigma$ & $\theta$ \\
\hline \\
1.2 & 4 
\end{tabular}
\end{table}

# My estimator beats your estimator

## Put all you work here

One could put all the text in a single `.Rmd` file.

## Or in separate files

```{r, child='example_child.Rmd'}
```

# How to cite

You can also cite other papers.

## rmarkdown syntax

You cite articles using `rmarkdown` syntax (google rmarkdown for helpful hints). For example, @halmos1970howto is a good text read. Or writing about mathematics is challenging [@halmos1970howto].




