---
title: "Example Dissertation"
author: "Bradley Saul"
date: "June 22, 2017"
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: UNC_thesis_template.tex
    includes: 
      in_header: example_header_include.tex
bibliography: example.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is an example thesis .Rmd template, which, when compiled, uses the `UNC_thesis_template.tex` file to create both a `.tex` file and a `.pdf` file.

NOTE: `UNC_thesis_template.tex` is under development and does NOT (yet) meet the UNC graduate school guidelines.

You can put custom definitions in a file to be included in the .tex header. For example, putting 
```
\def\cA{{\mathcal{A}}} 
```
in `example_header_include.tex`  allow you to type `\cA` in the text which, when compiled, yields: $\cA$. Change the filename as necessary but be sure to update the filename in the YAML header.

# Chapter 2

One could put all the text in a single `.Rmd` file.

# Chapter 3

```{r, child='example_child.Rmd'}
```

## How to make Citations 

You cite articles using `rmarkdown` syntax (google rmarkdown for helpful hints). For example, @halmos1970howto is a good text read. Or writing about mathematics is challenging [@halmos1970howto].

# References


